First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2016-09-02 eg6-letters/coherent/HeliumCohDVCS.tex
Update letter

Insert FIGURE DVCS nuclei
%\label{fig:DVCS}
\begin{figure}[htbp]
\caption{\label{fig:DVCS} Coherent DVCS}
\includegraphics[width=8.6cm]{DVCS.png}
\end{figure}

@@

In order to insure the coherence of the process, we detect all the products
of the reaction. The electron is detected by the CLAS, using the drift chamber 
to reconstruct its trajectory and the combination of the Cherenkov counters
and electromagnetic calorimeter to

we built a small and light 
radial time projection chamber (RTPC) depicted in figure~\ref{fig:rtpc} to 
detect the recoiling helium nuclei. this detector is placed directly ouside of 
our gaseous target filled with 6~atm helium. 
% to complete

\begin{figure}[htbp]
\caption{\label{fig:rtpc} RTPC description}
\includegraphics[width=8cm]{RTPC.png}
\end{figure}

%\section{DVCS Events Selection}

Detection, PID des particules.

\begin{figure*}[htbp]
\caption{\label{fig:exclu} Exclusivity cuts}
\includegraphics[width=17.2cm]{all_coh_exc_cuts.png}
\end{figure*}

@@

% This is mainly to compare to existing models
Generalized ratios (figure~\ref{fig:GenR})

\begin{figure}[htbp]
\caption{\label{fig:GenR} Generalized ratio}
\includegraphics[width=7.5cm]{coh_emc_Q2.png}
\includegraphics[width=7.5cm]{coh_emc_t.png}
\includegraphics[width=7.5cm]{coh_emc_xB.png}
\end{figure}

>>>>

Insert FIGURE DVCS nuclei
%\label{fig:DVCS}
\begin{figure}[htbp]
\caption{\label{fig:DVCS} Diagram for the coherent DVCS in the plane wave approximation.}
\includegraphics[width=8.6cm]{DVCS.png}
\end{figure}

@@

\begin{figure*}[tbp]
\caption{\label{fig:exclu} Exclusivity cuts}
\includegraphics[width=17.2cm]{all_coh_exc_cuts.png}
\end{figure*}

In order to insure the coherence of the process, we detect all the products
of the reaction. The electron detected by the CLAS, using the drift chamber 
to reconstruct its trajectory, while the combination of the Cherenkov counters
and electromagnetic calorimeter signals insure that it is not mistaken with
a negative pion. The high energy photon is detected in a PbWO calorimeter 
placed close to the beam line. Finally, we built a small and light 
radial time projection chamber (RTPC) to 
detect the recoiling helium nuclei. The chamber is placed directly ouside of 
a gaseous target filled with 6~atm helium-4 and is 20 cm long with a 3 cm radial
drift length.

%\begin{figure}[htbp]
%\caption{\label{fig:rtpc} RTPC description}
%\includegraphics[width=8cm]{RTPC.png}
%\end{figure}

%\section{DVCS Events Selection}
Explain exclusivity cuts

@@
